### 2024-10-21 analysis/analysis.qmd
arousal analysis included

### Valence: Best model

@@

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))

@@

```{r}
#R_studies <- read.csv("R_studies.csv")
R_summary <- read.csv("R_summary.csv")

@@

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))

### Sub-division based on techniques

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)

S<-summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
print(S)
```

### Sub-division based on journals (engineering vs psych)

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
```

### Sub-division based on N features

```{r}
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
dim(tmp)
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

### Sub-division based on N features and genres

```{r}
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
dim(tmp)
m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
infan <- InfluenceAnalysis(m.cor)
print(eggers.test(m.cor))
```

```{r}
#| eval: false
#| echo: false
outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")

@@

@@

To show the quality differences between core and eliminated studies.

```{r}
tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
#tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)

fp = ggplot(NULL) +
  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
  geom_text_repel(aes(x = SE, y = Zr, label=studies), data=tmpdata,size=2.5,max.overlaps = 40)+
  xlab('Standard Error') + ylab('Correlation')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_hline(yintercept = estimate, linetype='solid', color='grey50',linewidth=0.2) +
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
  scale_y_continuous(breaks=seq(0.0,1.00,0.20),limits=c(0.0,1.00),expand=c(0.00,0.00))+
  coord_flip()+
  theme_bw()
print(fp)
```

```{r}
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

### Arousal: Best model

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
#tmp <- dplyr::filter(R_studies,dimension=="arousal")
dim(tmp)
#tmp <- tmp[!is.na(tmp$values),]
dim(tmp)
#tmp<-drop_na(tmp)

m.cor <- metacor(cor = valuesMax, 
                 n = stimulus_n,
                 studlab = citekey,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

print(m.cor)
```
### Trimmed analysis
```{r}
O <- find.outliers(m.cor)
```

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))
plot(eggers.test(m.cor))
```

```{r}
#| eval: false
meta <- metagen(valuesMax, sqrt(valuesMax), 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")
find.outliers(meta)
infan <- InfluenceAnalysis(meta)
print(eggers.test(meta))

```{r}
update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)

forest(m.cor_subgroups,subgroup=TRUE)
```

```{r}
#| eval: false
g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
   geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
   coord_flip()+
   theme_bw()
g1

# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
# g<-ggplot(S,aes(y=maxvalue))+
#   geom_histogram(bins = 14)+
#   #facet_wrap(.~studyREF)+
#   coord_flip()+
#   theme_bw()
# g
```

>>>>

### Valence

@@

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))
```

@@

```{r}
R_summary <- read.csv("R_summary.csv")

@@

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))
```

### Explore heterogeneity

```{r}
#| eval: true
#| echo: true
# Method 1: Give us the Egger's test about beta coefficient from funnel
print(eggers.test(m.cor))

# Method 2: Find the impact to the results when removing those outside the 95CI
O <- find.outliers(m.cor) # 13 remaining out of 24
print(O)
# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
#infan <- InfluenceAnalysis(m.cor)

# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
thres<-quantile(m.cor$seTE,0.1)
ind<-m.cor$seTE<=as.numeric(thres)
m.cor10pct <- update(m.cor, subset = which(ind))

# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
pcurve(m.cor)
```

### Visualise (forest and funnel plots)

@@

### Sub-divisions

#### Sub-division based on techniques

```{r,results='asis'}
S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)
```

#### Sub-division based on journals (engineering vs psych)

```{r,results='asis'}
S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor2)
```

#### Sub-division based on N features

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

#### Sub-division based on N features and genres

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values

S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

### Arousal

```{r}
R_studies <- read.csv("R_studies.csv")
tmp <- dplyr::filter(R_studies,dimension=="arousal")
#if all studies, remove two with NA values
tmp <- tmp[!is.na(tmp$values),]
#dim(tmp)

# Take all models
m.cor <- metacor(cor = values,     # values 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

@@

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))
```

```{r}
R_summary <- read.csv("R_summary.csv")

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
#tmp <- dplyr::filter(R_studies,dimension=="valence")
#dim(tmp)

# Max values
m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF,#citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))
```

### Explore heterogeneity

```{r}
#| eval: true
#| echo: true
# Method 1: Give us the Egger's test about beta coefficient from funnel
print(eggers.test(m.cor))

# Method 2: Find the impact to the results when removing those outside the 95CI
O <- find.outliers(m.cor) # 13 remaining out of 24
print(O)
# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
#infan <- InfluenceAnalysis(m.cor)

# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
thres<-quantile(m.cor$seTE,0.1)
ind<-m.cor$seTE<=as.numeric(thres)
m.cor10pct <- update(m.cor, subset = which(ind))

# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
pcurve(m.cor)
```

### Visualise (forest and funnel plots)

### Sub-divisions

#### Sub-division based on techniques

```{r,results='asis'}
S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)
```

#### Sub-division based on journals (engineering vs psych)

```{r,results='asis'}
S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor2)
```

#### Sub-division based on N features

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

@@

#### Sub-division based on N features and genres

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values

S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

### 2024-10-21 manuscript/_figure2.qmd
arousal analysis included

```{r}
#| label: fig2
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest and funnel plots of valence predictions from the MER models.

library(metafor, warn.conflicts = FALSE)
library(dmetar,warn.conflicts = FALSE)
library(meta,warn.conflicts = FALSE)
library(DescTools,warn.conflicts = FALSE)
library(ggplot2,quietly = TRUE)
library(ggrepel,quietly = TRUE)

@@

#### Forest plot using forestplot
library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = m.cor$TE.common,
                lower = m.cor$lower.common,
                upper = m.cor$upper.common,
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(m.cor$TE.common,2),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
)
)

>>>>

```{r}
#| label: fig2
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest (A) and funnel (B) plots of the best valence models from all MER studies.

library(metafor, warn.conflicts = FALSE)
library(dmetar,warn.conflicts = FALSE)
library(meta,warn.conflicts = FALSE)
library(DescTools,warn.conflicts = FALSE)
library(ggplot2,quietly = TRUE)
library(ggrepel,quietly = TRUE)
library(forestplot)

@@

#### Forest plot using forestplot
data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
data<-dplyr::arrange(data,mean)

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = FisherZInv(m.cor$TE.random),
                lower = FisherZInv(m.cor$lower.random),
                upper = FisherZInv(m.cor$upper.random),
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(FisherZInv(m.cor$TE.random),3),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
)
)

### 2024-10-21 manuscript/_figure3.qmd
arousal analysis included

R_summary <- read.csv("../analysis/R_summary.csv")
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")

# Max values
m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF,#citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 #                 backtransf = TRUE,
                 #                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

#### Forest plot using forestplot
library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = m.cor$TE.common,
                lower = m.cor$lower.common,
                upper = m.cor$upper.common,
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(m.cor$TE.common,2),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
)
)

>>>>

R_summary <- read.csv("../analysis/R_summary.csv")
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")

# Max values
m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF,#citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 #                 backtransf = TRUE,
                 #                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

#### Forest plot using forestplot
library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
data<-dplyr::arrange(data,mean)

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = FisherZInv(m.cor$TE.random),
                lower = FisherZInv(m.cor$lower.random),
                upper = FisherZInv(m.cor$upper.random),
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(FisherZInv(m.cor$TE.random),3),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
)
)

### 2024-10-21 manuscript/manuscript.qmd
arousal analysis included

Since there are many models contained within each of the studies, we will report the results in two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study. The best performing model is the model within each study with the highest correlation coefficient. This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article. Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study. The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019]. We used Paule-Mandel estimator for between-study heterogeneity [@langan2019comparison] and Knapp-Hartung [@knapp2003improved] adjustments for confidence intervals. In this table we also report two subgroup analyses. One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into five modelling techniques introduced earlier (Table 1).

@@

Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal. Table 3 and Figure 3 show the same outputs as was done for valence describing the broad pattern of results in tabular format, and visually illustrate the spread and heterogeneity of all studies.

Table 3 indicates that the overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855). If we examine all the models, the correlation drops to 0.796, only marginally lower.

The indicators of heterogeneity ($\tau^2$ = 0.155 and $I^2$=96.8%) suggest high

@@

| Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
| Arousal      |             | 0.7959 \[0.7666; 0.8218\] | 29.0 | 0.0001 | 0.0676   | 95.6% |
| Arousal Max  | 24,15660    | 0.8070 \[0.7453; 0.8550\] | 10.3 | 0.0001 | 0.155    | 96.8% |
| *N Features* |             |                           |      |        |          |       |
| \<18 F       |             |                           |      |        |          |       |
| 18-260 F     |             |                           |      |        |          |       |
| 260+ F       |             |                           |      |        |          |       |
| *Techniques* |             |                           |      |        |          |       |
| KS           |             |                           |      |        |          |       |
| LM           |             |                           |      |        |          |       |
| FD           |             |                           |      |        |          |       |
| NN           |             |                           |      |        |          |       |
| RF           |             |                           |      |        |          |       |

<!-- {{< include _figure3.qmd >}} -->

Summarise here the pattern of results

>>>>

Since there are many models contained within each of the studies, we will report the results in two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study. The best performing model is the model within each study with the highest correlation coefficient. This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article.

### Results for valence

Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study for valence. The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019]. We used Paule-Mandel estimator for between-study heterogeneity [@langan2019comparison] and Knapp-Hartung [@knapp2003improved] adjustments for confidence intervals. In this table we also report two subgroup analyses. One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into five modelling techniques introduced earlier (Table 1).

@@

### Results for arousal

Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal. Table 3 describes the broad pattern of results in tabular format, and Figure 3 illustrates the spread and heterogeneity of all studies for arousal. The overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855). If we examine all the models reported in each study, the correlation drops marginally, to 0.784 (CI95% 0.765-0.801), despite this analysis includes about five times as many models as taking the best model out of each study. For arousal, even the baseline models seem to be performing on a relative high level. However, the indicators of heterogeneity are again high ($\tau^2$ = 0.155 and $I^2$=96.8%), which suggests that summary may be misleading. However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.787 95%CI -4.61-6.18, _t_ = 0.286, _p_ = 0.778). If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 14 studies in the summary that has _r_ = 0.8182 (95%CI 0.802-0.833) with $\tau^2$ = 0.0038 and $I^2$ = 76.0%. In other words, no material difference to the results obtained with all 24 studies.

@@

| Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
| Arousal All  | 126, 74365  | 0.7837 \[0.7652-0.8009\]  | 45.2 | 0.0001 | 0.064    | 96.3% |
| Arousal Max  | 24, 15660   | 0.8070 \[0.7453-0.8550\]  | 14.8 | 0.0001 | 0.128    | 97.7% |
| *N Features* |             |                           |      |        |          |       |
| \<18 F       | 5, 3036     | 0.8111 \[0.5342-0.9308\]  |      |        | 0.1815   | 98.9% |
| 18-260 F     | 11, 7318    | 0.5477 \[0.3434-0.7025\]  |      |        | 0.1331   | 97.6% |
| 260+ F       | 7, 4562     | 0.6845 \[0.5660-0.7752\]  |      |        | 0.0435   | 97.2% |
| *Techniques* |             |                           |      |        |          |       |
| KS           | 2, 2582     | 0.8068 \[0.5493-0.9244\]  |      |        | 0.0022   | 70.0% |
| LM           | 8, 1762     | 0.8812 \[0.8079-0.9277\]  |      |        | 0.0846   | 93.3% |
| FD           | 6, 4993     | 0.8077 \[0.6437-0.9008\]  |      |        | 0.1125   | 98.0% |
| NN           | 4, 2249     | 0.5339 \[0.3281-0.6912\]  |      |        | 0.0190   | 85.8% |
| RF           | 4, 4074     | 0.8024 \[0.7672-0.8327\]  |      |        | 0.0012   | 52.7% |

The forest plot in Figure 3 reveals

The subdivision of studies shows...

{{< include _figure3.qmd >}}
